The Second Data Release of the INT Photometric H$\alpha$ Survey of the Northern Galactic Plane (IPHAS DR2)

### 2014-03-12 paper/iphas-dr2.tex
Comment on (180, 3)

>>>>

Each of the sightlines reveals a stellar population
with distinct characteristics.
Firstly, towards the Galactic anti-centre at $l=180^\circ$ (Fig.~\ref{fig:l180}) 
we find a population dominated by lowly-reddened main sequence stars.
This is consistent with the estimated total sightline extinction of $E(B-V)=0.49$
given by \cite{Schlegel1998}, following the correction of \cite{Schlafly2011}.
Looking in more detail we can see that the stellar locus is narrower for M-type dwarfs than for earlier types;
we do not observe M dwarfs expereincing the strongest reddening possible for this sightline.
This implies that extinction is still increasing at distances beyond $\sim 2$~kpc,
where M dwarfs are too faint to be contained in the IPHAS catalogue.
It is also clear that there are no unreddened stars earlier than $\sim$K0 visible,
such stars would be saturated if within a few hundred parsecs.
This therefore suggests that there is a measurable increase in extinction locally.
We also note an relative absence of late type giants which,
due to the relative brevity of the corresponding phase of stellar evolution,
would only account for a small proportion of a volume limited sample.

In contrast, closer towards the galactic
centre at $l=45^\circ$ (Fig.~\ref{fig:l45})
we find a wealth of reddened objects
which appear to be separated into a lowly
and a highly reddened component,
perhaps revealing two distinct parts of the Galaxy.

Finally, in one of our earliest sightlines at $l=30^\circ$
we find a very high number of extremely reddened giants
in addition to an unreddened population
of foreground dwarfs.

The number density of stars in the colour-colour
and colour-magnitude space
can be compared against population synthesis models
to create three-dimensional maps of the extinction
across several kpc \citep{Sale2009,Sale2012}.
Such an extinction map based on our catalogue
is to be released in a separate paper
that accompanies this data release (Sale et al., in preparation).

\end{document}\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{amssymb,amsmath}
\usepackage[pdftex]{graphicx}
\usepackage{longtable} 
%\usepackage{lscape}
\usepackage{float}
\usepackage{booktabs}
\usepackage{aas_macros}
